rotation_runs2019

### 2019-10-16 inst/documents/rotation_runs2019.Rmd
correcting couple bugs insecticide switching

@@

nscenarios <- 100
plotyn <- 1 #allow turning plots on and off from here

# still deciding how best to do this ...
# infile_multi <- 'rotations-experiments-creating-201909.xlsx'
# infile_multi <- system.file("extdata", infile_multi, package = "rotations", mustWork = TRUE)
# inex_all <- read_excel(infile_multi)

# NOTE to add new files currently need to reinstall package because infiles are in extdata
#infile <- "expt-A2-freq-insame-costs-nodisp.csv"
# infile <- "expt-A4-freq-insame-costs-disp.csv"
# # get the id for the expot to include in outfilenames, specifies experiment attributes
# id_expt <- substr(infile,6,7)
# # read an experiment file specifying ranges
# inex <- read_in_expt(infile, nscenarios=nscenarios)

@@

@@

# text to go at start of document
cat("Experiment :",id_expt," scenario number is pagenum -1 \n\n    ")

>>>>

An rmarkdown document that can be modified and knit to run scenarios within a specified experiment.
Output files are saved to the specified outFolder.

@@

nscenarios <- 100
plotyn <- 1 #allow turning plots on and off from here, may want to turn plots off if doing large number of runs

@@

# old ways of doing it
# infile_multi <- 'rotations-experiments-creating-201909.xlsx'
# infile_multi <- system.file("extdata", infile_multi, package = "rotations", mustWork = TRUE)
# inex_all <- read_excel(infile_multi)

# older way with individual experiment files
# to add new files currently need to reinstall package because infiles are in extdata
# infile <- "expt-A2-freq-insame-costs-nodisp.csv"
# infile <- "expt-A4-freq-insame-costs-disp.csv"
# # get the id for the expot to include in outfilenames, specifies experiment attributes
# id_expt <- substr(infile,6,7)
# # read an experiment file specifying ranges
# inex <- read_in_expt(infile, nscenarios=nscenarios)

@@

# text to go at start of document
cat("\nThere are 16 potential experiments :\n\n    ")

cat("Experiment :",id_expt," scenario number is pagenum -1 \n\n    ")
